---
title: "Assignment 2"
author: "Asad"
date: "16/10/2022"
output: html_document
---

## STAT341 Assignment 2
1a) 
hoopR: A utility for working with Men's Basketball Data
wehoop: A utility for working with Women's Basketball Data
1b)
```{r}
library(hoopR)
load_nba_player_box()
```
1c)
```{r}
NbaData = read.csv("C:/Users/Asad Developer/Downloads/NBA_Player_Boxscore_2021-22.csv")
table(NbaData$team_abbreviation)
```
A typical team has 800-1000 rows dedicated to it in the dataset.
DUR (12 rows) and LEB (11) have an unusually low number of rows in the dataset.
There are a total of 27802 rows in the dataset

1d)
```{r}
npb = read.csv("C:/Users/Asad Developer/Downloads/NBA_Player_Boxscore_2021-22.csv")
npb2 = subset(npb, team_abbreviation != "DUR" & team_abbreviation != "LEB" )
dim(npb)
dim(npb2)
```
The new Dataset has 27779 rows while the original had 27802 rows.

## Question 2

2a)
```{r}
par(mfrow=c(1,3))
hist(npb2$reb, xlab="Rebounds per player-game", main="Frequency of Rebounds",
     breaks=  floor(log2(nrow(npb2))+1))
boxplot(npb2$reb)
plot(npb2$reb, ylab="Rebounds per player-game")
```
The histogram is left-skewed. It shows that there are more player-games with lower numbers of rebounds.
The box plot gives us additional information about the data. For example it tells us the median is around 2.5.
Lastly the quantile plot has many instances between 0-10 and then for 10 and above rebounds there is much less. The quantile plot may be misleading 
